Automated Formal Synthesis of Safe Digital Controllers\\ for Continuous Plants

### 2018-05-10 automatica/paper.tex
section 4
consensus on how to write counterexample guided inductive synthesis

%% Using state of the art verifiers, we evaluate these models against
%% automatically synthesised controllers using CEGIS-based synsthesis that
%% incorporate the above mentioned artifacts in different models of
%% Single-Input/Single-Output (SISO) systems.
In this paper we present two novel approaches for the synthesis of
digital controllers, both of which make use of the framework known as CounterExample-Guided
Inductive Synthesis (CEGIS)~\cite{jha-icse10,
  DBLP:conf/asplos/Solar-LezamaTBSS06}, 
  \note{we need to agree on how to spell out CEGIS}
a technique from formal methods that has recently shown much promise and which we export in this work to a control-theoretical setup.  
CEGIS is an iterative process, where each iteration performs inductive
generalisation based on counterexamples provided by a verification
oracle \note{see Figure xxx}. The inductive generalisation uses information 
about a limited number of inputs to compute a candidate solution
for the entire range of possible inputs. Our two instantiations of CEGIS are described next.

@@

\textbf{CEGIS --} Program synthesis is the problem of computing
correct-by-design programs from high-level specifications. Algorithms
for this problem have made substantial progress in recent years, in
particular CEGIS, which is a recent approach to inductive synthesis
borrowing ideas from Counter-Example Guided Abstraction Refinement
(CEGAR)~\cite{DBLP:conf/cav/ClarkeGJLV00} and
superoptimisation~\cite{DBLP:conf/iclp/BrainCVF06,
  DBLP:conf/asplosss/Massalin87}.  
\note{might be confusing that we relate the CEGAR architecture also to Abstract Acceleration?}   
This approach uses an iterative
process \note{cf. Fig. XX}, where each iteration performs inductive generalisation based
on counterexamples provided by a verification oracle.  In the absence
of complete specifications, oracles are queried to distinguish between
non-equivalent
programs~\cite{jha-icse10,DBLP:conf/fmcad/AlurBJMRSSSTU13}.

@@

%-------------------------------
\subsection{Description of the benchmarks}
\label{exp:benchmarks}
%-------------------------------

>>>>

%% Using state of the art verifiers, we evaluate these models against
%% automatically synthesised controllers using CEGIS-based synsthesis that
%% incorporate the above mentioned artifacts in different models of
%% Single-Input/Single-Output (SISO) systems.
In this paper we present two novel approaches for the synthesis of
digital controllers, both of which make use of the framework known as counterexample guided
inductive synthesis (CEGIS)~\cite{jha-icse10,
  DBLP:conf/asplos/Solar-LezamaTBSS06}, 
  a technique from formal methods that has recently shown much promise and which we export in this work to a control-theoretical setup.  
CEGIS is an iterative process, where each iteration performs inductive
generalisation based on counterexamples provided by a verification
oracle \note{see Figure xxx}. The inductive generalisation uses information 
about a limited number of inputs to compute a candidate solution
for the entire range of possible inputs. Our two instantiations of CEGIS are described next.

@@

\textbf{CEGIS --} Program synthesis is the problem of computing
correct-by-design programs from high-level specifications. Algorithms
for this problem have made substantial progress in recent years, in
particular CEGIS, which is a recent approach to inductive synthesis
borrowing ideas from counterexample guided abstraction refinement
(CEGAR)~\cite{DBLP:conf/cav/ClarkeGJLV00} and
superoptimisation~\cite{DBLP:conf/iclp/BrainCVF06,
  DBLP:conf/asplosss/Massalin87}.  
\note{might be confusing that we relate the CEGAR architecture also to Abstract Acceleration?}   
This approach uses an iterative
process \note{cf. Fig. XX}, where each iteration performs inductive generalisation based
on counterexamples provided by a verification oracle.  In the absence
of complete specifications, oracles are queried to distinguish between
non-equivalent
programs~\cite{jha-icse10,DBLP:conf/fmcad/AlurBJMRSSSTU13}.

@@

%-------------------------------
\subsection{Description of the control benchmarks}
\label{exp:benchmarks}
%-------------------------------
